Effect of character correlation

### 2017-09-19 Analysis/EffectCorrelationStats.Rmd
Updated stats

>>>>

```{r, echo = FALSE}
library(knitr)
library(xtable)
```

```{r, warning = FALSE}
## Pooling the data per scenarios
scenario_RF_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "RF", best = "norm")
scenario_Tr_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "Tr", best = "norm")

## Preparing the table labels
metric.labels <- c("RF", "", "", "Tr", "", "")

## Combining the data into a table
scenarios <- pool.table(list(scenario_RF_norm, scenario_Tr_norm),  metric.label = metric.labels,
                        label.param = "scenario")
```

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_scenarios <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled scenarios.")

```{r, eval = FALSE, echo = FALSE}
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Tab_pooledscenarios")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ scenario, fun = lm)
## Removing the null tests
results[[1]] <- results[[1]][-c(3,4),]
```

```{r, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(scenario_list, metric.label = metric.labels)
```

```{r, warning = FALSE}
## Pooling the data per character
character_RF_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "norm")
character_Tr_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "norm")

## Preparing the table labels
metric.labels <- c("RF", "", "", "Tr", "", "")

## Combining the data into a table
characters <- pool.table(list(character_RF_norm, character_Tr_norm), metric.label = metric.labels,
                         label.param = "character")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ character, fun = lm)
## Removing the null tests
results[[1]] <- results[[1]][-c(3,4),]
```

```{r, eval = FALSE, echo = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 3, label = "Tab_signif")
```

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(character_list, metric.label = metric.labels)
```

```{r, warning = FALSE}
## Pooling the data per taxa
taxa_RF_norm <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "RF", best = "norm")
taxa_Tr_norm <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "Tr", best = "norm")

## Preparing the table labels
metric.labels <- c("RF", "", "", "Tr", "", "")

## Combining the data into a table
taxa <- pool.table(list(taxa_RF_norm, taxa_Tr_norm), metric.label = metric.labels,
                   label.param = "taxa")
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(taxa, caption = captions_pooled_taxa, label = "Tab_pooledtaxa")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ taxa, fun = lm)
## Removing the null tests
results[[1]] <- results[[1]][-c(3,4),]
```

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm)
metric.labels <- c("RF", "", "", "Tr", "", "")
test_table <- pair.test.table(taxa_list, metric.label = metric.labels)
```

```{r, warning = FALSE}
## Pooling the data per taxa
method_RF_norm <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "RF", best = "norm")
method_Tr_norm <- multi.pool(whole_data, param =c("bayesian", "parsimony"),
                               metric = "Tr", best = "norm")

## Preparing the table labels
metric.labels <- c("RF", "", "Tr", "")

## Combining the data into a table
methods <- pool.table(list(method_RF_norm, method_Tr_norm), metric.label = metric.labels,
                      label.param = "method")
```

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ method, fun = lm)
## Removing the null tests
results[[1]] <- results[[1]][-c(3,4),]
```

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm)
metric.labels <- c("RF", "", "Tr", "")
test_table <- pair.test.table(methods_list, metric.label = metric.labels)
```

# Combined results

```{r}
## Summarising the data
sum_RF_best <- apply.test(whole_data, "RF", "norm", NULL)
sum_Tr_best <- apply.test(whole_data, "Triples", "norm", NULL)
```

## Printing the tables
kable(sum_RF_best, row.names = FALSE, caption = captions_summary[1])
kable(sum_Tr_best, row.names = FALSE, caption = captions_summary[2])
```

## Tables
make.xtable(sum_RF_best, caption = captions_summary[1], label = labels_summary[1])
make.xtable(sum_Tr_best, caption = captions_summary[2], label = labels_summary[2])
```

```{r}
## Applying an lm to all the data with error
results <- test.effect.aov(whole_data, fun = lmer,
                           formula = NTS ~ scenario + (1|method) + (1|taxa) + (1|character))
## Removing the null tests
results[[1]] <- results[[1]][-c(3,4),]
```

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff)
bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff)

## Tables
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_Tr_best, row.names = FALSE, digit = 3)
```

```{r, echo = FALSE}
## Setting the table captions
captions_bc <- paste0("Bhattacharrya Coefficient (",rep(c("Robinson-Fould distance", "Triplets distance"), 1) ," from the ",c(rep("best", 2)), " tree)" , " between the different scenarios.")

## Printing the tables
kable(bc_RF_best, row.names = FALSE, caption = captions_bc[1], digit = 3)
kable(bc_Tr_best, row.names = FALSE, caption = captions_bc[2], digit = 3)
```

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_bc <- paste0("Tab_BC", rep(c("RF", "Tr")), c(rep("best", 2)))

## Tables
make.xtable(bc_RF_best, caption = captions_bc[1], label = labels_bc[1])
make.xtable(bc_Tr_best, caption = captions_bc[2], label = labels_bc[2])
```

```{r, warning = FALSE}
## Running the pairwise Wilcox tests:
wx_RF_best <- apply.test(whole_data, "RF", "norm", wilcox.test)
wx_Tr_best <- apply.test(whole_data, "Triples", "norm", wilcox.test)

## Applying Bonferroni correction
for(column in c(5,7,9)) {
  wx_RF_best[,column] <- p.adjust(wx_RF_best[,column], method = "bonferroni")
  wx_Tr_best[,column] <- p.adjust(wx_Tr_best[,column], method = "bonferroni")
}
```

```{r, echo = FALSE}
## Setting the table captions
captions_wx <- paste0("Non-parametric Wilcoxon test (",rep(c("Robinson-Fould distance", "Triplets distance")) ," from the ",c(rep("best", 2)), " tree)" , " between the different scenarios (p-values corrected using Bonferroni-Holm correction).")

## Printing the tables
kable(wx_RF_best, row.names = FALSE, caption = captions_wx[1], digit = 3)
kable(wx_Tr_best, row.names = FALSE, caption = captions_wx[2], digit = 3)
```

```{r, echo = FALSE, eval = FALSE}
## Labels
labels_wx <- paste0("Tab_BC", rep(c("RF", "Tr")), c(rep("best", 2)))

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1])
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2])
```
